Make any stupid plot you want

### 2021-01-13 draft/sections/math.tex
sections

\subsubsection{Section}
\label{sec:section_data}
%% add context
The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & B \arrow[u, "f"', bend right]
    \end{tikzcd}
\end{equation}

such that $f$ is the right inverse of $\pi$
\begin{equation}
    \label{eq:section_domain}
    \pi(f(k)) = k \text{ for all } k \in K 
\end{equation}

In a trivial fiber bundle, $E = K \times F$ \cite{rowlandFiberBundle,FiberBundle2020}:
\begin{equation}
    \label{eq:section_return}
f(b) = (b, g(b))
\end{equation}

where the domain of $g(b)$ is $F_b$ and returns a point $p$ in $F_b$. The space of all possible sections $f$ of $E$ is $\Gamma(E)$. All sections $f \in \Gamma(E)$ have the same fibers $F$ and connectivity $K$. 
\paragraph{Example}
%%talk about table and all that jazz

For each field $c \in C$, the record function $r: C \rightarrow U_{\sigma}$ returns an object of type $\sigma(c) \in DT$. The set of all records $\Gamma(\sigma)$ is the set of all sections on $U_\sigma$. Spivak defines the $\tau$ mapping from an index of databases $K$ to records $\Gamma(\sigma)$ as $\tau: K \rightarrow \Gamma(\sigma)$. This is equivalent to $\tau: k \rightarrow E$ since $F = \Gamma(\sigma)$ and $F$ is the embedding in $E$ on which the records $r$ lie.

>>>>

\subsubsection{Section}
\label{sec:section_data}
The sections of the fiber bundles are the instances of the data. They are the functions that map from a key on $K$ to a set of values in $F$. For example, if we have a database, the section is the table that yields a row given an index. The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}

such that in a trivial fiber bundle, $E = K \times F$ \cite{rowlandFiberBundle,FiberBundle2020}:
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (x_{F_{0}}, \ldots, x_{F_{n}}))
\end{equation}
which we can also decompose such that
\begin{align}
\tau_{0}(k) &= (k, (x_{F_{0}}))\\
            & \vdotswithin{=}\\
\tau_{n}(k) &= (k, (x_{F_{n}}))
\end{align}

which allows us to have field wise access to the data so long as there is a shared $K$.
